\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-30 syntax.tex
Reply comments and update.

The reason we need this additional type construct of $\cC\sigma$ here is
to support \textit{code reuse}, as the rule of linkages hinders its
ability to do abstraction. Concretely speaking, (using surface syntax)
we don't have \\ $\goodTerm{\Gamma, \cL(\{a~:~\bW \sigma; b~:~a \to
T\})}{h}{\cL(\{a~:~\cU; b~:~a \to T\})}$\footnote{If we had one,
consider the case $T$ is bottom type and $\sigma$ is empty record and
thus $a$ is initially bottom type. Now we further override $h.a$ using
unit type we can derive inconsistency\YZ{You are talking about
overriding here, but you haven't told the reader what overriding means
in your metatheory.}}. This term is important for us to abstract the
concrete inductive type so that the later field can depend on the
abstract interface and achieve \textit{code reuse}. On the other hand,
we do have $\goodTerm{\Gamma, (\Sigma a : \bW\sigma, a \to T)
}{h}{(\Sigma a : \cU, a \to T)}$ because of the rule for existential
(also existential type just don't allow overriding\YZ{Why is it desired that this type in the context does not allow overriding (since it already says 'a : U')?}).
Thus to allow abstraction happens, we need $\cC\sigma$ to compile a
linkage to module as a part of the context and we also need
\ruleref{Lnkg Compile} to specify the compilation from linkage to
module.

@@

Sealing judgement is still about the important term $h$ we mentioned
earlier. Thanks to $\cC$, a newly added term $t_{new}$\YZ{By 'a newly
added term', do you mean a term that follows field 'a'?} is now in the
context containing $\cC\{a : \bW \sigma; ..\}$.
But if we want $t_{new}$ to be inherited(reused) when $\sigma$ is
extended, we would like $t_{new}$ to be in the context containing
$\cC\{a : \cU; ..\}$ instead. The sealing is responsible for this
because we have a sealing $\goodTerm{\Gamma, \cC\{a : \bW \sigma;
..\}}{s}{\cC\{a : \cU; ..\}}$ = $\goodTerm{\Gamma, (\Sigma a : \bW
\sigma,..)}{s}{(\Sigma a : \cU,..)}$. Then we can construct
$t_{new}$ in the context containing $(\Sigma a : \cU,..)$, ready for
inheritance.
Apparently $t_{new}$ in this case cannot be doing \textit{exhaustiveness
checking}, but it can freely use any \textit{exhaustiveness-checked}
recursor.\YZ{It occurs to me that you use the word "sealing" to mean
different (though tangentially related) things. Previously you used it
as in "sealed families".}\EDJreply{They are actually the same thing.
This sealing in metatheory is much stronger than that of the implemented
plugin. Downside of the strong sealing is that if the user really use
this version of sealing, the user will have to annotate what the sealed
family type is. Now in the plugin, the sealed family type is almost
fixed (directly inferred using a fixed rules). So basically this
complete version of sealing (in metatheory) can deduce that of seal (in
plugin implementation) }

>>>>

The reason we need this additional type construct of $\cC\sigma$ here is
to support \textit{code reuse}, as the rule of linkages hinders its
ability to do abstraction. Concretely speaking, (using surface syntax)
we don't have \\ $\goodTerm{\Gamma, \cL(\{a~:~\bW \sigma; b~:~a \to
T\})}{h}{\cL(\{a~:~\cU; b~:~a \to T\})}$\footnote{If we had one,
consider the case $T$ is bottom type and $\sigma$ is empty record and
thus $a$ is initially bottom type. Now the direct projection using \ruleref{Sig Proj} $\goodTerm{\Gamma, a : \cU}{h.b}{a \to \bot}$ will lead to problem because every field in linkage has this implicit universal quantification, and for this case we can substitute $a$ with arbitrary type, say $\top$: $\goodTerm{\Gamma}{h.b[a \mapsto \top]}{\top \to \bot}$ is a contradiction\YZ{You are talking about
overriding here, but you haven't told the reader what overriding means
in your metatheory.}\EDJreply{Ok. I use the projection now instead.}}. This term is important for us to abstract the
concrete inductive type so that the later field can depend on the
abstract interface and achieve \textit{code reuse}. On the other hand,
we do have $\goodTerm{\Gamma, (\Sigma a : \bW\sigma, a \to T)
}{h}{(\Sigma a : \cU, a \to T)}$ because of the rule for existential
(also existential type just don't allow overriding\YZ{Why is it desired that this type in the context does not allow overriding (since it already says 'a : U')?}).
Thus to allow abstraction happens, we need $\cC\sigma$ to compile a
linkage to module as a part of the context and we also need
\ruleref{Lnkg Compile} to specify the compilation from linkage to
module.

@@

Sealing judgement is still about the important term $h$ we mentioned
earlier. Thanks to $\cC$, a newly added field $t_{new}$ after $a$ \YZ{By 'a newly
added term', do you mean a term that follows field 'a'?}\EDJreply{Thanks. Fixed} is now in the
context containing $\cC\{a : \bW \sigma; ..\}$.
But if we want $t_{new}$ to be inherited(reused) when $\sigma$ is
extended, we would like $t_{new}$ to be in the context containing
$\cC\{a : \cU; ..\}$ instead. The sealing is responsible for this
because we have a sealing $\goodTerm{\Gamma, \cC\{a : \bW \sigma;
..\}}{s}{\cC\{a : \cU; ..\}}$ = $\goodTerm{\Gamma, (\Sigma a : \bW
\sigma,..)}{s}{(\Sigma a : \cU,..)}$. Then we can construct
$t_{new}$ in the context containing $(\Sigma a : \cU,..)$, ready for
inheritance.
Apparently $t_{new}$ in this case cannot be doing \textit{exhaustiveness
checking}, but it can freely use any \textit{exhaustiveness-checked}
recursor.\YZ{It occurs to me that you use the word "sealing" to mean
different (though tangentially related) things. Previously you used it
as in "sealed families".}\EDJreply{They are actually the same thing.
This sealing in metatheory is much stronger than that of the implemented
plugin. Downside of the strong sealing is that if the user really use
this version of sealing, the user will have to annotate what the sealed
family type is. Now in the plugin, the sealed family type is almost
fixed (directly inferred using a fixed rules). So basically this
complete version of sealing (in metatheory) can deduce that of seal (in
plugin implementation) }
